Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-06-11 latex/acl2019.tex
Small fix

%%% INCREMENTATION %%%
%% Instances
\subsection{Experiment 1: Number of instances}
Figure \ref{fig:inc_node}(a) shows that the incease in performance is not
proportional to the number of worker which differ form what we would expect; it even
decrease when we reach 8 workers. This is explained by an increase in IO overhead
corrolated to the number of workers (Figure \ref{fig:inc_node}(b)), as more worker
access the nfs simultaneously it increase the stress put on the system which result
in bottleneck, errors and slow down.

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_instances.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_instances.png}%
    }
    \caption{125 splits, 10 iterations, 4 sec. sleep delay}
    \label{fig:inc_node}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_iterations.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_iterations.png}%
    }
    \caption{125 splits, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_itr}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_sleeptime.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_sleeptime.png}%
    }
    \caption{125 splits, 10 iterations, 8 instances}
    \label{fig:inc_sleep}
\end{figure}

% Chunks
\subsection{Experiment 1: Number of splits}
In Figure \ref{fig:inc_splits} Spark is not compared for 30 chunks. This is because
spark has a 2GB limitation in the task size it can compute. Note from Figure
\ref{fig:inc_splits}(b) that the compute time increase when there is more splits.
This is expected because the sleep delay is constant throughout this experiment and
there are more compute task when the number of splits increases. We also note that in
Figure \ref{fig:inc_splits}(b) for 30 splits the dask bag api has a much lower
overhead time. This is because we only calculate the idle time of used core and the
dask bag api was only using one thread per block in comparison to the dask delayed
and dask futures api which were offloading the calculations on multiple thread of a
same worker. From Figure \ref{fig:inc_splits} we observe that when the dataset is
seperated in more (smaller) splits it saves IO time however it increases the overhead
by a similar amount; the inverse happens when we reduce teh number of splits.

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_splits.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_splits.png}%
    }
    \caption{10 iterations, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_splits}
\end{figure}

From the Figures \ref{fig:inc_node} to \ref{fig:inc_chunk} the Dask bag with optimized graph
has high variance on its makespan. Moreover, Dask API seems to always offer a better
option than spark RDDs.

@@

\begin{figure}[htp]
    \centering
    \subfloat[Dask execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_dask-bag_baseline_gantt.png}%
    }

    \subfloat[Spark execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_spark_baseline_gantt.png}%
    }
    \caption{125 splits, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_gantt}
\end{figure}

@@

    \subfloat[Histogram total time]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_idle_instances.png}%
    }
    \caption{8 instances}
    \label{fig:histo_instance}
\end{figure}

\subsection{Experiment 2: Number of splits (task size)}

@@

    \subfloat[Histogram total time]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_idle_splits.png}%
    }
    \caption{10 iterations, 4 sec. sleep delay, 8 instances}
    \label{fig:histo_splits}
\end{figure}

@@

\subsection{Experiment 3: Number of subjects}

>>>>

%%% INCREMENTATION %%%
%% Instances
\subsection{Experiment 1: Number of instances}
Figure \ref{fig:inc_worker}(a) shows that the incease in performance is not
proportional to the number of worker which differ form what we would expect; it even
decrease when we reach 8 workers. This is explained by an increase in IO overhead
corrolated to the number of workers (Figure \ref{fig:inc_worker}(b)), as more worker
access the nfs simultaneously it increase the stress put on the system which result
in bottleneck, errors and slow down.

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_worker.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_worker.png}%
    }
    \caption{125 splits, 10 iterations, 4 sec. sleep delay}
    \label{fig:inc_worker}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_itr.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_itr.png}%
    }
    \caption{125 splits, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_itr}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_sleep.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_sleep.png}%
    }
    \caption{125 splits, 10 iterations, 8 instances}
    \label{fig:inc_sleep}
\end{figure}

% Chunks
\subsection{Experiment 1: Number of splits}
In Figure \ref{fig:inc_chunk} Spark is not compared for 30 chunks. This is because
spark has a 2GB limitation in the task size it can compute. Note from Figure
\ref{fig:inc_chunk}(b) that the compute time increase when there is more splits.
This is expected because the sleep delay is constant throughout this experiment and
there are more compute task when the number of splits increases. We also note that in
Figure \ref{fig:inc_chunk}(b) for 30 splits the dask bag api has a much lower
overhead time. This is because we only calculate the idle time of used core and the
dask bag api was only using one thread per block in comparison to the dask delayed
and dask futures api which were offloading the calculations on multiple thread of a
same worker. From Figure \ref{fig:inc_chunk} we observe that when the dataset is
seperated in more (smaller) splits it saves IO time however it increases the overhead
by a similar amount; the inverse happens when we reduce teh number of splits.

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_chunk.png}%
    }

    \subfloat[Incrementation total time]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_idle_chunk.png}%
    }
    \caption{10 iterations, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_chunk}
\end{figure}

From the Figures \ref{fig:inc_worker} to \ref{fig:inc_chunk} the Dask bag with optimized graph
has high variance on its makespan. Moreover, Dask API seems to always offer a better
option than spark RDDs.

@@

\begin{figure}[htp]
    \centering
    \subfloat[Spark execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/spark_inc_baseline_gantt.png}%
    }

    \subfloat[Dask bag execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/dask_bag_inc_baseline_gantt.png}%
    }

    \subfloat[Dask delayed execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/dask_delayed_inc_baseline_gantt.png}%
    }

    \subfloat[Dask futures execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/dask_futures_inc_baseline_gantt.png}%
    }
    \caption{125 splits, 4 sec. sleep delay, 8 instances}
    \label{fig:inc_gantt}
\end{figure}

@@

    \subfloat[Histogram total time]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_idle_instances.png}%
    }
    \caption{8 instances}
    \label{fig:histo_wroker}
\end{figure}

@@

    \subfloat[Histogram total time]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_idle_splits.png}%
    }
    \caption{10 iterations, 4 sec. sleep delay, 8 instances}
    \label{fig:histo_chunk}
\end{figure}

@@
